### 2011-04-23 docs/architecture/architecture.tex
fix directory structure -- docs/ was shown in the wrong place
some updates

 BoxLib is a library for describing meshes consisting of a union
 of boxes.  The BoxLib modules define the basic datatypes used
 in MAESTRO.

@@

\item {\tt doc/}

 Documentation describing the basic algorithm.

@@

@@

   Several sub-directories containing routines to generate
   1D initial conditions in hydrostatic equilibrium for 
   mapping onto the MAESTRO grid.  See \S~\ref{sec:initial_models}
   for details.

@@

  The generic Makefiles that store the compilation flags for
  various platforms.

@@

A large number of runtime parameters affect the code's behavior.  Any
runtime parameter can be set either in the inputs file, as {\tt parameter
  = value} or on the command line by adding {\tt --parameter value} after
listing the inputs file on the command line.  A full list of runtime
parameters is detailed in \S~\ref{sec:runtime_parameters}.  Below we
outline the most common runtime parameters.

@@

\item {\tt restart} tells MAESTRO to restart from a checkpoint.  The
      value of this parameter should be the file number to restart from.

@@

Note that grid cells must be square, i.e. $\Delta x = \Delta y = \Delta z$
where $\Delta x$ on the base grid is computed as $({\tt prob\_hi\_x}
- {\tt prob\_lo\_x})/{\tt n\_cellx}$.

@@

Several useful analysis scripts (written in Fortran 90) can be found
in {\tt fParallel/data\_processing}.  The {\tt GNUmakefile} there
needs to be edited to indicate which of the tools to build.  These
routines are described in \S~\ref{sec:analysis}.

@@

@@

A MAESTRO application is built from several pacakges (the
multigrid solver, an EOS, a reaction network, etc.).  The core
MAESTRO packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := extern/EOS/helmeos   
CONDUCTIVITY_DIR := extern/conductivity/constant
NETWORK_DIR := extern/networks/ignition

>>>>

 BoxLib is a library for describing meshes consisting of a union
 of boxes.  The BoxLib modules define the basic datatypes used
 in MAESTRO.  BoxLib also provides the routines that handle the
 parallelization and I/O.

@@

@@

 \item {\tt docs/}

   Documentation describing the basic algorithm (including this
   document).

   Several sub-directories containing routines to generate
   1-d initial conditions in hydrostatic equilibrium for 
   mapping onto the MAESTRO grid.  See \S~\ref{sec:initial_models}
   for details.

@@

@@

  The generic Makefiles that store the compilation flags for
  various platforms.  Platform/compiler-specific options are stored
  in the {\tt comps/} subdirectory.

@@

A large number of runtime parameters affect the code's behavior.  Any
runtime parameter can be set either in the inputs file, as {\tt parameter
  = value}, or on the command line by adding {\tt --parameter value} after
listing the inputs file on the command line.  A full list of runtime
parameters is detailed in \S~\ref{sec:runtime_parameters}.  Below we
outline the most common runtime parameters.

@@

\item {\tt restart} tells MAESTRO to restart from a checkpoint.  The
      value of this parameter should be the file number to restart from.
      For example, to restart from the checkpoint file {\tt chk00010},
      you would set {\tt restart = 10}.

@@

Note that grid cells must be square, i.e. $\Delta x = \Delta y = \Delta z$
where $\Delta x$ on the base grid is computed as $({\tt prob\_hi\_x}
- {\tt prob\_lo\_x})/{\tt n\_cellx}$.  For multilevel problems, the effective
number of zones on the finest grid in the $x$ direction will be
${\tt n\_cellx} \cdot 2^{({\tt max\_levels} -1)}$.

@@

Several useful analysis scripts (written in Fortran 90) can be found
in {\tt fParallel/data\_processing}.  The {\tt GNUmakefile} there
needs to be edited to indicate which of the tools to build.  For
example, to extract the density along a line from the center of a
plotfile, {\tt plt00200}, in the $y$-direction:

\begin{verbatim}
fextract.Linux.gfortran.exe -d 2 -v "density" -p plt00200
\end{verbatim}

These routines are described in \S~\ref{sec:analysis}.

@@

  Particle data is stored separately from the fluid data.  Instead
  of being part of the plotfiles, the particle data is outputted
  each timestep into files named {\tt timestamp\_*}, where 
  the number indicates which processor did the writing.  These
  particle files can be processed and the particle data plotted
  using the python routines in {\tt data\_processing/python/}.

@@

A MAESTRO application is built from several packages (the
multigrid solver, an EOS, a reaction network, etc.).  The core
MAESTRO packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := extern/EOS/helmeos   
CONDUCTIVITY_DIR := extern/conductivity/constant
NETWORK_DIR := extern/networks/ignition
